---
title: "QA Log"
output: html_document
params:
  id: NA
  name: NA
  version: NA
  leadanalyst: NA
  analyticalassurer: NA
  BCM: NA
  totalscore: NA
  DGscore: NA
  SCscore: NA
  VEscore: NA
  VAscore: NA
  DAscore: NA
  DGchecks: NA
  number_DG: NA
  SCchecks: NA
  number_SC: NA
  VEchecks: NA
  number_VE: NA
  VAchecks: NA
  number_VA: NA
  DAchecks: NA
  number_DA: NA
---

<style>
.column-left{
  float: left;
  width: 33%;
  text-align: left;
}
.column-center{
  display: inline-block;
  width: 33%;
  text-align: center;
}
.column-right{
  float: right;
  width: 33%;
  text-align: right;
}
</style>


Project ID
```{r, echo=FALSE, comment=""}
writeLines(params$id)
```

Project title
```{r, echo=FALSE, comment=""}
writeLines(params$name)
```

Version
```{r, echo=FALSE, comment=""}
writeLines(params$version)
```

Lead analyst
```{r, echo=FALSE, comment=""}
writeLines(params$leadanalyst)
```

Analytical assurer
```{r, echo=FALSE, comment=""}
writeLines(params$analyticalassurer)
```

Business Critical (Y/N)
```{r, echo=FALSE, comment=""}
writeLines(params$BCM)
```

Scores:

Overall score:
```{r, echo=FALSE, comment=""}
writeLines(paste(params$totalscore,"%"))
```

Documentation and Governance:
```{r, echo=FALSE, comment=""}
writeLines(paste(params$DGscore,"%"))
```

Structure and Clarity:
```{r, echo=FALSE, comment=""}
writeLines(paste(params$SCscore,"%"))
```

Verification:
```{r, echo=FALSE, comment=""}
writeLines(paste(params$VEscore,"%"))
```

Validation:
```{r, echo=FALSE, comment=""}
writeLines(paste(params$VAscore,"%"))
```

Data and Assumptions:
```{r, echo=FALSE, comment=""}
writeLines(paste(params$DAscore,"%"))
```

Documentation and Governance breakdown:

```{r, echo=FALSE, comment=""}
listDG <- list(1:params$number_DG)

readDG <- function(number){cat(params$DGchecks[number])}

html(lapply(listDG,readDG))
```

Structure and Clarity breakdown:

```{r, echo=FALSE, comment=""}
listSC <- list(1:params$number_SC)

readSC <- function(number){cat(params$SCchecks[number])}

lapply(listSC,readSC)
```

Verification breakdown:

```{r, echo=FALSE, comment=""}
listVE <- list(1:params$number_VE)

readVE <- function(number){cat(params$VEchecks[number])}

lapply(listVE,readVE)
```

Validation breakdown:

```{r, echo=FALSE, comment=""}
listVA <- list(1:params$number_VA)

readVA <- function(number){cat(params$VAchecks[number])}

lapply(listVA,readVA)
```

Data and Assumptions breakdown:

```{r, echo=FALSE, comment=""}
listDA <- list(1:params$number_DA)

readDA <- function(number){cat(params$DAchecks[number])}

lapply(listDA,readDA)
```
