---
title: "QA Log"
output: html_document
params:
  id: NA
  name: NA
  version: NA
  leadanalyst: NA
  analyticalassurer: NA
  BCM: NA
  totalscore: NA
  DGscore: NA
  SCscore: NA
  VEscore: NA
  VAscore: NA
  DAscore: NA
  DGchecks: NA
  number_DG: NA
  SCchecks: NA
  number_SC: NA
  VEchecks: NA
  number_VE: NA
  VAchecks: NA
  number_VA: NA
  DAchecks: NA
  number_DA: NA
---

<style>
.column-left{
  float: left;
  width: 33%;
  text-align: left;
}
.column-center{
  display: inline-block;
  width: 33%;
  text-align: center;
}
.column-right{
  float: right;
  width: 33%;
  text-align: right;
}
</style>

Project ID
```{r, echo=FALSE}
params$id
```

Project title
```{r, echo=FALSE}
params$name
```

Version
```{r, echo=FALSE}
params$version
```

Lead analyst
```{r, echo=FALSE}
params$leadanalyst
```

Analytical assurer
```{r, echo=FALSE}
params$analyticalassurer
```

Business Critical (Y/N)
```{r, echo=FALSE}
params$BCM
```

Scores:

Overall score:
```{r, echo=FALSE}
paste(params$totalscore,"%")
```

Documentation and Governance:
```{r, echo=FALSE}
paste(params$DGscore,"%")
```

Structure and Clarity:
```{r, echo=FALSE}
paste(params$SCscore,"%")
```

Verification:
```{r, echo=FALSE}
paste(params$VEscore,"%")
```

Validation:
```{r, echo=FALSE}
paste(params$VAscore,"%")
```

Data and Assumptions:
```{r, echo=FALSE}
paste(params$DAscore,"%")
```

Documentation and Governance breakdown:

```{r, echo=FALSE}
listDG <- list(1:params$number_DG)

readDG <- function(number){cat(params$DGchecks[number])}

lapply(listDG,readDG)
```

Structure and Clarity breakdown:

```{r, echo=FALSE}
listSC <- list(1:params$number_SC)

readSC <- function(number){cat(params$SCchecks[number])}

lapply(listSC,readSC)
```

Verification breakdown:

```{r, echo=FALSE}
listVE <- list(1:params$number_VE)

readVE <- function(number){cat(params$VEchecks[number])}

lapply(listVE,readVE)
```

Validation breakdown:

```{r, echo=FALSE}
listVA <- list(1:params$number_VA)

readVA <- function(number){cat(params$VAchecks[number])}

lapply(listVA,readVA)
```

Data and Assumptions breakdown:

```{r, echo=FALSE}
listDA <- list(1:params$number_DA)

readDA <- function(number){cat(params$DAchecks[number])}

lapply(listDA,readDA)
```
