---
title: "QA Log"
output: html_document
params:
  id: NA
  name: NA
  version: NA
  leadanalyst: NA
  analyticalassurer: NA
  BCM: NA
  totalscore: NA
  DGscore: NA
  SCscore: NA
  VEscore: NA
  VAscore: NA
  DAscore: NA
  DGchecks: NA
  SCchecks: NA
  VEchecks: NA
  VAchecks: NA
  DAchecks: NA
---

<style>
.column-left{
  float: left;
  width: 33%;
  text-align: left;
}
.column-center{
  display: inline-block;
  width: 33%;
  text-align: center;
}
.column-right{
  float: right;
  width: 33%;
  text-align: right;
}
</style>


Project ID: `r params$id`

Project title: `r params$name`

Version: `r params$version`

Lead analyst: `r params$leadanalyst`

Analytical assurer: `r params$analyticalassurer`

Business Critical (Y/N): `r params$BCM`

Scores:

Overall score: `r paste(params$totalscore,"%")`

Documentation and Governance: `r paste(params$DGscore, "%")`

Structure and Clarity: `r paste(params$SCscore, "%")`

Verification: `r paste(params$VEscore, "%")`

Validation: `r paste(params$VAscore, "%")`

Data and Assumptions: `r paste(params$DAscore, "%")`

```{r, echo=FALSE, comment=""}

allDG <- paste(unlist(params$DGchecks),collapse='<br />')

```

Documentation and Governance breakdown:

`r allDG`


Structure and Clarity breakdown:

```{r, echo=FALSE, comment=""}

allSC <- paste(unlist(params$SCchecks),collapse='<br />')

```

`r allSC`

Verification breakdown:

```{r, echo=FALSE, comment=""}

allVE <- paste(unlist(params$VEchecks),collapse='<br />')

```

`r allVE`

Validation breakdown:

```{r, echo=FALSE, comment=""}

allVA <- paste(unlist(params$VAchecks),collapse='<br />')

```

`r allVA`

Data and Assumptions breakdown:

```{r, echo=FALSE, comment=""}

allDA <- paste(unlist(params$DAchecks),collapse='<br />')

```

`r allDA`
