---
title: "QA Log"
output: html_document
params:
  id: NA
  name: NA
  version: NA
  leadanalyst: NA
  analyticalassurer: NA
  BCM: NA
  DGscore: NA
  DG1: NA
  DG2: NA
  DG3: NA
  DG4: NA
  DG5: NA
  DG6: NA
  DG7: NA
  DG8: NA
---

<style>
.column-left{
  float: left;
  width: 33%;
  text-align: left;
}
.column-center{
  display: inline-block;
  width: 33%;
  text-align: center;
}
.column-right{
  float: right;
  width: 33%;
  text-align: right;
}
</style>

Project ID
```{r, echo=FALSE}
params$id
```

Project title
```{r, echo=FALSE}
params$name
```

Version
```{r, echo=FALSE}
params$version
```

Lead analyst
```{r, echo=FALSE}
params$leadanalyst
```

Analytical assurer
```{r, echo=FALSE}
params$analyticalassurer
```

Business Critical (Y/N)
```{r, echo=FALSE}
params$BCM
```

Documentation and Governance overall:
```{r, echo=FALSE}
params$DGscore
```

Documentation and Governance breakdown:

Scope and specification
```{r, echo=FALSE}
params$DG1
```

User guide

```{r, echo=FALSE}
params$DG2
```

Technical guide

```{r, echo=FALSE}
params$DG3
```

KIM

```{r, echo=FALSE}
params$DG4
```

Version control

```{r, echo=FALSE}
params$DG5
```

Responsibilities

```{r, echo=FALSE}
params$DG6
```

QA planning and resourcing

```{r, echo=FALSE}
params$DG7
```

Record of QA

```{r, echo=FALSE}
params$DG8
```