---
title: "Test_markdown"
output: html_document
params:
  id : NA
  website: NA
---

We can display the project ID number in a box like this

```{r, echo=FALSE, comment=""}
writeLines(params$id)
```


Or we can put project ID in line like this `r params$id`

Or we can put it on the next line like this, and it doesn't display in a box

`r params$id`

To include a hyperlink

```{r, echo=FALSE, comment=""}
params$website
```

Or try in line `r params$website`

Now, try defining something, and calling it later on

```{r, echo=FALSE, comment=""}
testdef <- "This is a test"
```

And now call it `r testdef`

Now try defining a web address

```{r, echo=FALSE, comment=""}
testweb <- "<a href=\"https://youtube.com\">\"https://youtube.com\"</a>"
```

And now call it `r testweb`

Now define text with line skips. 

Using n doesn't work in line, but it does work in box when we use the cat() function

```{r, echo=FALSE, comment=""}
testskip <- "This is the first line \n and this is the second line without cat()"

testskip1 <- "This is the first line \n and this is the second line with cat()"

testskip

cat(testskip1)
```

Using cat() in line gives us nothing: `r cat(testskip)`

If we just call without cat, we don't skip line: `r testskip`

Using br doesn't work in box, but it does work in line

```{r, echo=FALSE, comment=""}
testskip2 <- "This is the first line <br /> and this is the second line"

testskip2
```

We now get line skips in line: `r testskip2`

Now we test the lapply function, so create a function and a list to lapply over. First, call lapply within box

```{r, echo=FALSE, comment=""}
apply_fun <- function(inputs){
  paste("We are pasting the", inputs, "input")
}

apply_list <- c("first", "second", "third", "fourth")

lapply(apply_list,apply_fun)

```

Next, call lapply within line `r lapply(apply_list,apply_fun)`

Now, try the lapply function with a line skip

```{r, echo=FALSE, comment=""}
apply_fun1 <- function(inputs){
  paste("<br /> We are pasting the", inputs, "input")
}

lapply(apply_list,apply_fun1)

```

Call within line `r lapply(apply_list,apply_fun1)`

Finally, let's use the lapply function with a line skip and a hyperlink

```{r, echo=FALSE, comment=""}
apply_list1 <- c("<a href=\"https://bbc.co.uk\">\"https://bbc.co.uk\"</a>",
                 "<a href=\"https://youtube.com\">\"https://youtube.com\"</a>",
                 "<a href=\"https://reddit.com\">\"https://reddit.com\"</a>")

lapply(apply_list1,apply_fun1)
```

Call within line: `r lapply(apply_list1,apply_fun1)`